Ensemble Super-Learning for State Estimation. \\Application to the reconstruction of urban pollution.

### 2023-09-07 paper/main.tex
Numerical experiments in paper.

\asmodif{
Finally, another way to build a super-learner is by sequentially composing individual models $A_j$ together with transition functions $P_j$ and train them to correct the errors of previous ones so that 
$$
S_j(A_1, \dots, A_j) = P_j(\sigma_j^*) \circ A_j(\theta_j^*) \circ \dots \circ P_1(\sigma_1^*) \circ A_1(\theta_1^*)
$$
and $S=S_p$. At each step $j$ the target of each submodel is to correct the residuals $\tilde z_j=z - \cS_{j-1}(r, x)$ of previous steps, so $(z, r)\in Y^{M} \mapsto (\tilde z_j^{Y^{M}}, r) \in \tilde Y^{M}$. At the same time the information received from the pollution part of the input $x$ is also replaced by the last residual $x = (z, r^\obs, q, T, w) \in X^{M} \mapsto x_j^M = (\tilde z_j^{X^{M}}, r^\obs, q, T, w) \in \tilde X^{M}$ so the minimization problem in this step becomes
$$
\theta_j^* \in \underset{\theta_j \in \Theta_j}{\argmin}
\sum_{x_j^M, \tilde z_j^{Y^{M}}, r}
\Vert \tilde z_j^{Y^{M}} - A_j(\theta_j)(r, x_j^M)) \Vert^2_2.
$$
The transition maps $P_j$ are also trained to correct the residuals $\hat z_j=z - A_j(\theta_j^*)\circ\cS_{j-1}(r, x)$ of previous steps, so $(z, r)\in Y^{SL} \mapsto (\hat z_j^{Y^{SL}}, r) \in \hat Y^{SL}$ and $x = (z, r^\obs, q, T, w) \in X^{SL} \mapsto x_j^{SL} = (\tilde z_j^{X^{SL}}, r^\obs, q, T, w)  \in \hat X^{SL}$ so the minimization problem in this step becomes
$$
\sigma_j^* \in \underset{\sigma_j \in \Sigma_j}{\argmin}
\sum_{\hat z_j^{X^{SL}}, \hat z_j^{Y^{SL}}, r}
\Vert \hat z_j^{Y^{SL}} - P_j(\sigma_j)(\hat z_j^{X^{SL}}) \Vert^2_2.
$$
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial average}
The first, and simplest reconstruction mapping $A$ is a spatial average of the measurement observations. This will be taken as our baseline to compare against other more sophisticated reconstructions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Graph Features \om{[To Do: Streamline]}}

@@

>>>>

\asmodif{
Finally, another way to build a super-learner is by sequentially composing individual models $A_j$ together with transition functions $P_j$ and train them to correct the errors of previous ones so that 
$$
S_j(A_1, \dots, A_j) = P_j(\sigma_j^*) \circ A_j(\theta_j^*) \circ \dots \circ P_1(\sigma_1^*) \circ A_1(\theta_1^*)
$$
and $S=S_p$. At each step $j$ the target of each submodel is to correct the residuals $\tilde z_j=z - \cS_{j-1}(r, x)$ of previous steps, so $(z, r)\in Y^{M} \mapsto (\tilde z_j^{Y^{M}}, r) \in \tilde Y^{M}$. At the same time the information received from the pollution part of the input $x$ is also replaced by the last residual $x = (z, r^\obs, q, T, w) \in X^{M} \mapsto x_j^M = (\tilde z_j^{X^{M}}, r^\obs, q, T, w) \in \tilde X^{M}$ so the minimization problem in this step becomes
$$
\theta_j^* \in \underset{\theta_j \in \Theta_j}{\argmin}
\sum_{x_j^M, \tilde z_j^{Y^{M}}, r}
\Vert \tilde z_j^{Y^{M}} - A_j(\theta_j)(r, x_j^M)) \Vert^2_2.
$$
The transition maps $P_j$ are also trained to correct the residuals $\hat z_j=z - A_j(\theta_j^*)\circ\cS_{j-1}(r, x)$ of previous steps, so $(z, r)\in Y^{SL} \mapsto (\hat z_j^{Y^{SL}}, r) \in \hat Y^{SL}$ and $x = (z, r^\obs, q, T, w) \in X^{SL} \mapsto x_j^{SL} = (\tilde z_j^{X^{SL}}, r^\obs, q, T, w)  \in \hat X^{SL}$ so the minimization problem in this step becomes
$$
\sigma_j^* \in \underset{\sigma_j \in \Sigma_j}{\argmin}
\sum_{\hat z_j^{X^{SL}}, \hat z_j^{Y^{SL}}, r}
\Vert \hat z_j^{Y^{SL}} - P_j(\sigma_j)(\hat z_j^{X^{SL}}) \Vert^2_2.
$$
}{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial average}
\label{sec:snapshotmean}
The first, and simplest reconstruction mapping $A$ is a spatial average of the measurement observations. This will be taken as our baseline to compare against other more sophisticated reconstructions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Graph Features \om{[To Do: Streamline]}}
\label{sec:grpah_features}

@@

Following the methodollogy and using the data explained in the previous sections we put in comparison the following methods:
\begin{itemize}
\item \textbf{\perplexityinsert{average}}: our baseline as described in \cref{sec:snapshotmean}.
\item \textbf{\perplexityinsert{krigging}}:
\item \textbf{\perplexityinsert{lm}}: We use a Super-learner approach by sequentially combining 
	\begin{enumerate}
	\item The baseline: \perplexityinsert{average}.
	\item A Graph Feature extractor using traffic information from neighbouring edges up to distance $\perplexityinsert{kneighbours}$, as described in \cref{sec:grpah_features}, with a learnable linear transformation (applying first a z-score normalization and then fitting a Lasso \cite{}) trained to correct the residuals of the previous method in the concatenation.
	\end{enumerate}
	As transition functions for the ssequential supeer-learner we used a linear regression for the first transition and a Lasso for the second.

 we first perform a \perplexityinsert{average} our baseline as described in \cref{sec:snapshotmean}.
\item \textbf{\perplexityinsert{lmextra}}:
\item \textbf{\perplexityinsert{nn}}:
\item \textbf{\perplexityinsert{ensemble}}:
\end{itemize}
